Figures to insert in text

### 2018-04-08 Chapters/Introduction.tex
reprinted

A second and final qualification: It is my hope that readers of this thesis will accept the format of self-contained studies, as just as valid as a monograph on a particular topic.  With these qualifications, we are ready to venture into the world of computational management science.

>>>>

A second and final qualification: It is my hope that readers of this thesis will accept the format of self-contained studies, as just as valid as a monograph on a particular topic\footnote{e.g., a reference to the ``fundamental research theorem'', reprinted in the Appendix, seems inescapable.}.  With these qualifications, we are ready to venture into the world of computational management science.
